Thus far speckle has been described mathematically as a sum of random,
statistically independent phasors --- the random phasor sum of
\Equation{eqn:phasorsum}.  Such a process is in essence \textit{single
scattering}; only one scattering event occurs for each photon (or SPP) from
the source to detector.  However, a much more interesting and
phenomenologically complex situation arises when allowing higher order
scattering processes to take over.  Such a situation is, unsurprisingly, known
as \textit{multiple scattering}.

The transition from the single to the multiple scattering occurs roughly upon
fulfillment of the Ioffe-Regel criterion~\cite{ioffe1960non}, when the
transport mean free path $l^*$ is much larger than the spatial frequency of
the optical wave, or
\begin{equation}
k l^* \approx 1
\end{equation}
where $k=\omega/c$ as usual.  The transport mean path is defined as the
characteristic distance over which the incident wave is scattered out of
its incoming direction~\cite{berkovits1994correlations}.  This is the
optical analog of electron transport in condensed matter physics.  There,
one would use the Fermi wavenumber $k_F$ and take $l^*$ to be the mean free
path.  Materials for which $k_F l^* \gg 1$ are conductors, and materials
for which $k_F l^* \ll 1$ are insulators.  The multiple scattering regime can
also be defined in terms of the sample length $L$, such that if
$l^* \ll L$ and $1/(k l^*) \ll 1$, the system can be thought to be the
multiple scattering regime.  

How does one determine whether a system is in the single or multiple
scattering regime?
