Biosensors based on surface plasmon resonance play a central role as a
simple and remarkably responsive label-free method for characterizing and
quantifying biomolecular
interactions~\cite{homola1999surface}~\cite{homola2006surface}.  Amongst
the most popular of these sensors are those which excite localized surface
plasmon polaritons on thin metal films in prism coupled
configurations~\cite{hoa2007towards}.  These platforms, despite their
ubiquity and commercial success, are host to an amazing depth of useful
phenomena which has yet to be explored in the context of biosensing.  In
this work we detail investigations of single and multiply scattered surface
plasmon polaritons from such a system.  Specifically, we look at the
structure of the re-radiated optical field which contain additional
features such as near field self-interference, speckle, and optical
vorticies, and their relations to the scattering microstructure.  Our
results suggest several possible avenues for advancing the 
detection limits of surface plasmon based biosensors for both single
particles and bulk refractive index measurements.

A photon is a quantized oscillation of an electromagnetic field.  When this
field is in proximity to an interface such as the surface of a metal,
oscillations of free charge can be induced.  If the field is evanescent in
both directions orthogonal to the surface, the oscillations become
localized and are known as surface plasmons (SPs).  Furthermore, if
conditions exist such that the in-plane momentum and phase of the incident
photon and the surface plasmon match, the coupling produces a hybrid
excitation known as surface plasmon polariton (SPP).  An SPP is trapped on
this interface and propagates until it decays; either re-radiating as a
photon or being absorbed into the metal as heat.

SPPs, like photons, are quantum mechanical objects.  Because this system is
momentum-conserving, elastically scattered plasmons will preserve all the
information of their parent field.  

In the literature one will find a sense of integerchangability regarding
the terms ``plasmon'', ``surface plasmon'', ``localized surface plasmon'',
and ``surface plasmon polariton''.  To be clear, in this work we are always
refering to surface plasmon \textit{polaritons}: a surface plasmon which is
strongly coupled to the exciting electromagnetic field.  SPPs are a type of
quasiparticle, as they are essentially a collective excitation of free
electrons.  The fundamental point here is that strong coupling preserves
quantum mechanical information.

\subsection{Organization}
This work is roughly organized in the following way.
\Chapter{ch:existence} is what you are currently reading.  Here is laid out
theory, mathematical details regarding the conditions under which SPPs may
be excited, and physical properties.  In \Chapter{ch:experimental} we
describe all details regarding the physical experiment: construction,
protocols, , and data analysis.  These first two chapters form the
mathematical and physical basis for the remaining text.

Discussion of our studies and new results begins with \Chapter{ch:bulkri}.
Here, the bulk refractive index sensing properties of the cone are
described.  Closely related, \Chapter{ch:interference} discusses a newly
discovered interference phenomena in the cone and the possible utility in
the context of SPR refractive index sensing.

Perhaps one of the most interesting features of the cone is speckle, the
subject of \Chapter{ch:speckle}.  Here we compare the properties of cone
speckle with those of classic speckle fields in the context of
correlations, refractive index pertrubations, and multiple scattering
effects.

Finally, in \Chapter{ch:scatteringmicro} we look at the influence of the
cone speckle on the scattering microstructure itself.
