\documentclass[a4paper]{article}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{pstricks}
\usepackage{pst-all}
% I had to download the latest source version of pst-eucl to get
% \pstMarkAngle to work properly
\usepackage{pst-eucl}
\usepackage{psfrag}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{textcomp}
\usepackage{siunitx}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage[abs]{overpic}

% make typing infinite integrals easy
\newcommand{\intinfty}{\int_{-\infty}^{\infty}}
\newcommand{\micron}{\micro\meter}

% roman numerals
\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\begin{document}

\title{With Greatly Limited Resources\\
	Part II: Surface Plasmon Random Scattering}
\author{Aaron Webster}
\date{\today}

\maketitle
%\tableofcontents

\section{Overview}
In the following document I will give a brief account of some of the things
we looked at last winter.  It is in no way comprehensive, and focuses
mainly on certain aspects of weirdospace I believe we have a good
explanation for.

Section \ref{sec:simulation} deals with the numerical simulation, and to
that accord two programs were written: a Monte Carlo simulation and an
analytic counterpart.  Both programs were written to some degree by Bert,
so there is certainly overlap in the results, but there were some errors
and limitations I hope to have addressed.  This section should also serve
to succinctly document the programs and the rationale behind their
function.

The way plasmon scattering is implemented in the Monte Carlo simulation
leads to some interesting statistical distributions of scatterers and their
paths.  Section \ref{sec:stats} deals with this topic and some possible
connections with other scattering theories.

Following, Section \ref{sec:explain} attempts to give an explanation of
the features found in both simulation and experiment.  It also makes what I
feel is a strong case for the observation of coherent backscattering.

The remaining sections are miscellany that didn't fit in anywhere else.
They are presented mostly as results without a lot of commentary.
Finally, the Appendix includes the larger figures and comparisons from
previous sections.

\section{Simulation}
\label{sec:simulation}
\input{simulation/simulation}
\section{Statistical Properties}
\label{sec:stats}
\input{stats/stats}
\section{Scattering Permutations}
\label{sec:permute}
\input{clevergrid/clevergrid}
\section{Explanation of Features in Weirdospace}
\label{sec:explain}
\input{events/events}
\section{Comparisons Between Experiment, Simulation, and Theory}
\input{compare/compare}
\input{appendix/appendix}
\input{radialac/radialac}

%\bibliographystyle{plain}
%\bibliography{writeup}
\end{document}
